---
title: "Dealing with directory and files"
author: "Nicolas BARTALUCCI, Ludovic CHAUMAZ"
date: "30/09/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
unlink('~/ETUDES/UGA/M2_BEE_DynaMO/UE_OIMM/CoursR_BEE2019/Directory_Files_cache', recursive = TRUE)
```

# We can use R to create, delete and move and obtain information on files and directories.

## Get and change the current working directory

- **getwd** function :
```{r getwd, echo = TRUE}
getwd()
```

- **setwd** function :
```{r setwd, echo = TRUE}
setwd("C:/Users/BARTALUCCI_Nicolas/Desktop/")
```


## Create files and directory

- **dir.create** function to create a folder :
```{r dir.create, echo = TRUE}
dir.create("Garden")
dir.create("Garden/Kitchen")
```
It is still possible to create a folder by giving the full path where we want to create it.

- **file.create** function to create a file :
```{r file.create, echo = TRUE, results="hide"}
file.create("Garden/Potatoe.txt") #text document
file.create("Garden/Banana.docx") #word document
file.create("Garden/Egg_plant.csv") #csv document
```

Thus, creating a lot of files is easy :
```{r sapply, echo = TRUE, results="hide"}
sapply(paste0("Garden/Vegetable_", 1:42,".txt"), file.create)
```

## Rename a file

- **file.rename** function :
```{r rename, echo=TRUE}
file.rename("Garden/Vegetable_22.txt","Garden/Truite.txt")
```


## How to move a file

- **file.move** from *filesstrings* library can be used :
```{r move, echo=TRUE}
#install.packages("filesstrings")
library(filesstrings)
file.move("Garden/Vegetable_11.txt", "Garden/Livingroom")
```


## Copying a file or folder

- **file.copy** function :
```{r copy, echo = TRUE}
file.copy("Garden/Banana.docx","Garden/Kitchen")
```
The second argument is the folder in which you want to duplicate the file.

## Listing files in a directory

- **list.files** function :
```{r listing, echo = TRUE}
list.files("Garden",
           recursive = TRUE, #if you want all the subdirectory files
           full.names = TRUE #to have the full names
           )
list.files("Garden",
           recursive = TRUE, #if you want all the subdirectory files
           pattern = ".csv")
```

Useful if you want to read in all the CSV files from a directory :
```{r csv, echo = TRUE}
#all_csv=lapply(list.files("Garden",pattern = ".csv"), read.csv)
```

## Get details about files

- **fileSnapshot** function for a directory :
```{r details, echo = TRUE}
snapshot=fileSnapshot("Garden")
head(snapshot$info)
```

- **file.info** function for a file :
```{r file.info, echo = TRUE}
file.info("Garden/Banana.docx")
```
To have seperated details you can also use **file.ctime** and **file.mtime** functions.

## Delete files

- **file.remove** and **unlink** functions :
```{r delete, echo = TRUE}
file.remove("Garden/Banana.docx")
unlink("Garden/Potatoe.txt")
unlink("Garden/Kitchen", recursive = TRUE)
```

## Check the existence of a directory or a file

- **file.exists** function :
- **file.remove** and **unlink** functions :
```{r exist, echo = TRUE}
file.exists(c("Garden/Egg_plant.csv","Garden/Vegetable_1.txt","Garden/Potatoe.txt"))
dir.exists(c("Garden","Garden/Kitchen", "Mountain"))
```

## Get other informations on a file

- **basename** function gives the basename :
```{r basename, echo = TRUE}
basename("Garden/Egg_plant.csv")
```
- **dirname** function gives the path of the directory :
```{r dirname, echo = TRUE}
dirname("Garden/Egg_plant.csv")
```
- **file_ext** function (*tools* package) gives the extension :
```{r extension, echo = TRUE}
library(tools) ; file_ext("Garden/Egg_plant.csv")
```
## Physically open a file or open a selection window

- **shell.exec** or **file.show** functions can be used :
```{r open, echo = TRUE}
#shell.exec("C:/Users/BARTALUCCI_Nicolas/Desktop/Garden/Vegetable_1.txt")
#file.show("Garden/Egg_plant.csv")
```

- **file.choose** function opens a selection window :
```{r selection window, echo = TRUE}
#file.choose()
```

```{r, include=FALSE}
unlink("Garden", recursive = TRUE)
```

