---
title: "Cours Latex/Sweave"
author: "Ludovic Chaumaz / Maxime Jaunatre"
date: "19 septembre 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

<!--Maxime & sweave-->

## Incorporer du code R

Lorem Ipsum

Lien vers la vignette Sweave :  <http://127.0.0.1:24054/library/utils/doc/Sweave.pdf>.

ou alors : 
```{r help}
trouver l'option pour voir vignette sweave
```

aide des options de chunks sweaves :
```{r}
help(RweaveLatex)
```

prefix.string > label > number
figures can be exported in a special directory if global sweave option says so...notion of compedium

can include files in tex, but won't process them , with `\imput` 
`\SweaveInput{}` process them or not?

`\Sexpr{expr}` add values in text or even code. But need to remove all braces

can put reference to chunks with `<<name>>`

This is `noweb` synthax but in fact there is a multitude of them

encoding is ASCII by default, but can't be greatly modified (see fontenc and inputenc)
encoding seem's tricky, to look further

default figure scale is `\setkeys{Gin}{width=0.8\textwidth}`
to modify it, insert same code afet `\begin{document}`

new  file is generated for each figure, so par() are to reset each time
need to create a function to set it as default, might be tricky as well

default figure output is pdf, can be change by  `<<figN, fig=TRUE, pdf=FALSE, png=TRUE>>`

Rtangle extract all code and form a .R apart (like maya did) (so there is no need to split = T)

ONLY ONE GRAPH PER CHUNK !  SO NO FOR LOOP FOR FIGURES
a way to hack it :
```
<<results=tex,echo=FALSE>>=
for(i in 1:4){
  fname <- paste("myfile", i, ".pdf", sep = "")
  pdf(file = fname, width = 6, height = 6)
  plot(rnorm(100)+i)
  dev.off()
  cat("\\includegraphics{", fname, "}\n\n", sep = "")
}
@
```

set line length in R :
`{r} options(width = 40)`

RTFMN!






